---
title: "River Statistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{River Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

# The RPRW R Package

## Loading the Package

First, install and load the RPRW package
```{r, eval = FALSE}
install.packages("RPRW")
library(RPRW)
```

```{r, echo = FALSE}
library(RPRW)
```

## The `river` data

We can inspect the `river` data, which contains length and discharge measurements for several rivers
```{r}
river
```

To learn more about the data, run `?river`.

## Using the Package

This R package is designed to summarize length and discharge for rivers whose names match a particular pattern. There are three functions:

1. `river_means()`, which summarizes the mean length and discharge
```{r}
river_means(river, "Mi|C")
```

To learn more about `river_means()`, run `?river_means`.

2. `river_medians()`, which summarizes the mean length and discharge for rivers whose names match a particular pattern
```{r}
river_medians(river, "Mi|C")
```

To learn more about `river_medians()`, run `?river_medians`.

3. `river_stat()`, which summarizes a general function of length and discharge for rivers whose names match a particular pattern
```{r}
river_stat(river, "Mi|C", min)
river_stat(river, "Mi|C", max)
```

To learn more about `river_stat()`, run `?river_stat`
