---
title: |
  A manuscript about rivers
author:
  - name: Michael Dumelle
    affil: a
    email: Dumelle.Michael@epa.gov
affiliation:
  - num: a
    address: |
      United States Environmental Protection Agency -
      200 SW 35th St, Corvallis, OR, 97333
bibliography: interactcadsample.bib
appendix: appendix.tex
abstract: |
  This abstract about rivers secretly describes that this document serves as a
  template for authors who are preparing a manuscript for a Taylor & 
  Francis journal using the \LaTeX\ document preparation system and the 
  `interact` class file, which is available via selected journals' home 
  pages on the Taylor & Francis website.
keywords: |
  River; Length; Discharge
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

# Introduction {#intro}

This is my introduction about rivers. Next we talk about the background, which I refer to here as Section \ref{background}. 

# Background {#background}

Rivers are neat. We wanted to study river length and discharge. Next we give subsections discussing both.

## Length {#subsec:length}

This is where I talk about river length.

## Discharge {#subsec:discharge}

This is where I talk about river discharge.

# Methods {#sec:methods}

This is where I talk about methods. It may include an equation like this one defining a mean
\begin{equation}\label{eq:mean}
  \bar{x} = \frac{1}{n}\sum_{i = 1}^n x_i
\end{equation}
I can refer to that equation as Equation \ref{eq:mean}.

# Analysis {#sec:analysis}

```{r, include = FALSE}
# this is my R setup chunk
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  echo = FALSE
)
```

```{r, message = FALSE, warning = FALSE}
library(RPRW)
library(xtable)
library(readr)
library(here)
```



```{r, message = FALSE, results = "asis"}
river_C <- river[, grep("C", names(river))]
river_C_table <- xtable(river_C, label = "tab:rivers_C", caption = "Rivers whose names start with C")
print(river_C_table, comment = FALSE)

min_df <- read_csv(here("inst", "output", "min_df"))
min_df_table <- xtable(min_df[, -1], label = "tab:rivers_min", caption = "Length and discharge minimums for rives whose names start with C")
print(min_df_table, inclue.rownames = FALSE, comment = FALSE)
```

The length minimum in Table \ref{tab:rivers_min} is `r min_df[["length_min"]]` kilometers. Further exploring the data, we present a plot of river length vs discharge in Figure \ref{fig:rivers}. 
```{r rivers, fig.align = "center", fig.cap = "River length vs discharge", out.width = "75%"}
plot(
  x = unlist(river["length", ]),
  y = unlist(river["discharge", ]),
  xlab = "length",
  ylab = "discharge"
)
```

# Discussion {#discussion}

This is where I talk about my take-home points.

# Data and Code Availability {-}

The data are available here. The R package are available here. This article was published using the rticles package [@rticles2021]. Some LaTeX knowledge will be helpful when using rticles.
